Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-08-25 paper/ms.tex
model correlation files and correlation_statistic.py

The second constraint  comes from the angular correlation function (ACF)
for all the models having the $15$ mock surveys consistent with
observations . The ACF is computed  ( using 
the Davis \& Peebles  estimator \citep{Davis1983} ) only on the densest
sub-field in all the 15 mock surveys corresponding to the SSA22
region. We then take the mean ACF over the 15  mock surveys  for
each model as well as its the standard deviation to include
the effect of cosmic variance.

We finally compare the observational ACF and the mean mock  ACF of the models   
in therms of the angular correlation length ($\theta_{0}$) by fitting 
them to a power-law function:

@@

Both mock and observational ACF are derived by a least
square minimization procedure. The observational errors of 
the ACF as well as the standard deviation of the mean modeled ACFs  are
considered to compute the error in the fitted parameters to ensure ourselves
to include poissonian and cosmic-variance errors. 
We consider that a model is consistent with observations if the two
parameters $\beta$ and $\theta_0$ are equal within a $1$-$\sigma$ range.

>>>>

The second constraint  comes from the angular correlation function (ACF)
for all the models having the $15$ mock surveys consistent with
observations . The ACF is computed  ( using 
the Landy \&  Szalay  estimator \citep{Landy1993} )  on $1$ the densest
and $2)$ a mean sub-field of each of the 15 mock surveys. This is done to 
compare the predicted ACFs with the \cite{Hayashino2004}  and \cite{Ouchi2010}
ACFs respectively.

The observational ACF and the  mock  ACF of the models are compared   
in therms of the angular correlation length ($\theta_{0}$) by fitting 
them to a power-law function:

@@

Both mock and observational ACF are derived by a least
square minimization procedure to the previous equation. The  errors of 
the ACF  are considered to compute the error in the fitted parameters to ensure ourselves
to include poissonian. At the same time, for each model ${\mathcal M}$ we 
compute the mean and standard deviation on the fitted parameters over
each mock survey to account for cosmic-variance errors. 
We consider that a model is consistent with observations if the two
parameters $\beta$ and $\theta_0$ are equal within a $1$-$\sigma$ range.
